%Préambule du document :
\documentclass[12pt]{lettre}
\usepackage[utf8]{inputenc}
\usepackage{babel} 
\usepackage{eurosym}%pour le symbole euro
%\usepackage{lipsum}
\usepackage{setspace}
\makeatletter
%\newcommand*{\NoRule}{\renewcommand*{\rule@length}{0}}
\makeatother 
\date{11 August, 2020}%si differente de celle du jour
 
%Corps du document
\begin{document}
\begin{letter}{
%Universit\'{e} Toulouse Capitole 1\\
%2, rue Doyen-Gabriel-Marty\\
%Toulouse cedex 9\\
%T\'{e}l. +33 (0)5 61 63 35 00\\
%E-Mail: www.ut-capitole.fr
International Finance Corporation (IFC)
}
\address{
 Alexandro Disla\\
25, carefour Ism\'{e}, impasse F\'{e}n\'{e}lon\\
Pernier 23} 
\email{alexandrodisla@hotmail.com}
\telephone{+50941483700}
\nofax{}
\lieu{Port-au-Prince}
\signature{}
%\signature{\begin{tabular}{@{}p{.5in}p{2in}@{}}
%		& \hrulefill \\
%		& \textbf{Alexandro Disla} \\
%		& Economiste-Planificateur au Minist\`{e}re de la Planification et de la Coop\'{e}ration Externe\\
%	\end{tabular}
%}

%\conc{Cover Letter}
 
\opening{Dear Sir or Madam,}

\begin{spacing}{1.5}

Applied economist and modeling analyst 
at the Directorate of Economic and Social Planning 
of the Ministry of Planning and Extern 
Cooperation, I would like to send you my 
application for the post of operations analyst 
at the International Finance Corporation based in Haiti.

After my baccalaureate in 2010, I was admitted to the Center for Planning and 
Applied Economics Techniques. A university 
center under the supervision of the said ministry, it is 
responsible for the training of young executives for the 
public administration, the banking sector and the private 
sector in matters of applied economy, planning and statistics. 
In 2014, after four years of study, I successfully completed 
all the courses according to the requirements set by the 
scientific council of the Center.

This rigorous training in applied economics gave me a solid 
foundation in statistics, economics and computer science. 
Which has developed in me, a capacity for understanding 
phenomena related to the completeness of the real world. 
And I learned that information literacy helps streamline 
decision-making. In my work environment, I was able to 
strengthen my capabilities in terms of basic data analytics, 
statistics  and modeling. My role is very diverse. I 
periodically monitor the various macroeconomic aggregates. 
I participate in the work of setting up the budget 
together with the Ministry of Economy and Finance. 
In addition, in the context of strengthening management 
and Modeling capacities, I work under the 
supervision of an European Union expert. We have worked together 
to set up an impact policy simulation model 
called: "Information and Development Planning Model". 
This model is called upon to serve the country in terms of 
good governance. We finished the work preliminary estimates.

Having said that, with my analytical and programming skills and 
experiences, I believe that I am capable of fulfilling the 
role of Operations Analyst for the IFC Country Office in Haiti (CLAHT). 
I would like to make my contribution to the development 
projects led by the institution. I express myself clearly and 
intelligibly in French and English. In addition, I have 
extensive knowledge of Microsoft Office, R, Python and 
JavaScript. I fully understand relational databases management
 system 
(RDMS) such as PostgreSQL and MySQL. And I know how to operate 
non-relational databases management system (NRDMS) like MongoDB.

I love working in a friendly work environment with dynamic 
colleagues. I take great pleasure in working on difficult 
projects but also participating in the decision-making processes. 
Finally, although this experience was occasional, I enjoyed 
working with foreign colleagues with diverse backgrounds. I 
would like to find myself again in such a rewarding and 
motivating environment.

\end{spacing}

\closing{
    While requesting your attention to my application, please 
    accept, Madam, Sir, the expression of my respectful 
    consideration.}
\end{letter}
\end{document}
