\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{helvet}

\name{Alexandro}{Disla}
\title{Analyst–Programmer | Data \& Backend Developer}
\address{Rue Saint-Louis Jeanty \#14, Route de Frère}{}{}
\phone[mobile]{(+509) 4148-3700}
\email{alexandrodisla@hotmail.com}
\extrainfo{GitHub: \url{https://github.com/AD0791}}

\begin{document}
\makecvtitle

\section{Professional Profile}
\cvitem{}{Versatile developer specialized in integration, automation, and data analysis, with over four years of experience in API development, database modeling, and business process optimization. Experienced in multi-system environments, I design and maintain reliable, well-documented, and secure IT solutions to support digital transformation and data-driven decision-making.}

\cvitem{Key Strengths}{
\begin{itemize}
    \item Development of secure, containerized RESTful APIs (Docker);
    \item Data automation and integration (SQL, ETL, Commcare, MySQL);
    \item Visualization and reporting (Plotly, Matplotlib, Power BI, Looker Studio, RMarkdown, Quarto);
    \item Documentation, version control, and collaboration (Git, DevOps mindset);
    \item Cloud experience (AWS, Google Cloud, BigQuery, Apache Beam);
    \item Analytical approach grounded in training in applied economics.
\end{itemize}}

\section{Professional Experience}
\cventry{Feb 2026 -- Present}{Software Engineer}{Tekkod LLC}{Remote}{}{
\begin{itemize}
    \item Lead the "STS Mobile App Modernization" project, upgrading React Native from 0.65.1 to 0.74.x.
    \item Migrated the architecture to Hermes engine, Java 17, and Gradle 8.8, enabling Bridgeless Mode.
    \item Performed a full migration to Firebase v22 (Modular API) and replaced deprecated notifications with @notifee/react-native.
    \item Conducted a Yoga 3.0 UI Audit to ensure layout consistency and React 18 compatibility.
    \item Refactored core components and fixed asynchronous state updates in RewardsModal.
    \item Update the looker studio dasboard to add search and filter capabilities.
\end{itemize}}

\cventry{Oct 2023 -- Jan 2026}{mWater \& Data Analyst Consultant}{HANWASH}{Remote (Upwork)}{}{
\begin{itemize}
    \item Part-time contract. Collaborated with the M\&E team to resolve data management issues from field collection via mWater.
    \item Designed and implemented dashboards to present results to stakeholders (Plotly, Matplotlib, Power BI, Looker Studio).
    \item Created and deployed mWater surveys compliant with JMP standards, aligned with the logical framework and indicator matrix.
    \item Produced training guides (PowerPoint) to help stakeholders and managers understand and use dashboards. Trained data entry teams on using the mWater mobile app.
\end{itemize}}

\cventry{Mar 2021 -- May 2024}{Backend Developer}{Tekkod LLC}{}{}{
\begin{itemize}
    \item Part-time contract. Developed RESTful web services following best practices.
    \item Implemented Docker containers and deployment pipelines. Secured APIs with JWT authentication.
    \item Applied repository pattern, documented endpoints, and versioned via Git.
    \item Built data pipeline to migrate MongoDB data to BigQuery via Apache Beam.
    \item Created and maintained Looker Studio dashboards. Contributed to frontend tasks for React and React Native projects.
\end{itemize}}

\cventry{Oct 2021 -- Aug 2024}{Monitoring \& Evaluation Officer}{Impact Youth Project, Caris Foundation International}{}{}{
\begin{itemize}
    \item Designed digital data collection forms integrated into Commcare / HIVHaiti.
    \item Automated activity tracking reports using Python and SQL.
    \item Developed REST endpoints for internal dashboards. Created and deployed weekly dashboards via AWS using RMarkdown and Quarto.
    \item Maintained EID Power BI dashboard with biweekly updates. Ensured data quality and automated MySQL integration.
\end{itemize}}

\cventry{Nov 2015 -- Mar 2021}{Software Development Consultant (UNOPS Project)}{CassionSoft}{}{}{
\begin{itemize}
    \item Developed a REST API service for form analysis with OAuth2 / JWT authentication.
    \item Implemented authorization strategies and complete technical documentation.
\end{itemize}}

\cventry{2014 -- 2015}{Economist}{Ministry of Planning and External Cooperation}{}{}{
\begin{itemize}
    \item Monitored macroeconomic indicators, contributed to public policy reports, and collaborated with modeling teams for socio-economic simulations.
\end{itemize}}

\section{Education}
\cvitem{2010--2014}{Advanced Studies Diploma in Applied Economics, C.T.P.E.A}
\cvitem{2009--2010}{High School Diploma (Philosophy, Honors), Institution Saint-Louis de Gonzague}
\cvitem{Self-learning}{FlatIronSchool, CodeWithMosh, Udemy}

\section{Technical Skills}
\cvitem{Languages \& Frameworks}{Python, FastAPI, SQLModel, SQLAlchemy, Pydantic, Pandas, Numpy, Plotly, Docker, Git, React, React Native}
\cvitem{Databases}{MySQL, PostgreSQL, SQL Server, MongoDB (Beanie, Pymongo), BigQuery}
\cvitem{Tools \& Automation}{Commcare, Streamlit, Power BI, Looker Studio, RMarkdown, Quarto, Apache Beam, AWS, Google Cloud, VS Code}
\cvitem{Methodologies}{CI/CD, API Documentation, Unit Testing, Monitoring \& Metrics, Data Integration (ETL)}
\cvitem{Languages}{French (fluent), English (fluent), Creole (native)}

\section{Distinctive Strengths}
\cvitem{}{Strong ability to quickly understand business processes and translate them into technical solutions.}
\cvitem{}{Commitment to code quality, security, and performance. Team spirit, rigor, and continuous curiosity for technology (AI, automation, Power Platform).}

\end{document}
