%PrÃƒÂ©ambule du document :
\documentclass[12pt]{lettre}
\usepackage[utf8]{inputenc}
\usepackage{babel} 
\usepackage{eurosym}%pour le symbole euro
%\usepackage{lipsum}
\usepackage{setspace}
\makeatletter
%\newcommand*{\NoRule}{\renewcommand*{\rule@length}{0}}
\makeatother 
\date{11 August, 2020}%si differente de celle du jour
 
%Corps du document
\begin{document}
\begin{letter}{
%Universit\'{e} Toulouse Capitole 1\\
%2, rue Doyen-Gabriel-Marty\\
%Toulouse cedex 9\\
%T\'{e}l. +33 (0)5 61 63 35 00\\
%E-Mail: www.ut-capitole.fr
International Finance Corporation (IFC)
}
\address{
 Alexandro Disla\\
25, carefour Ism\'{e}, impasse F\'{e}n\'{e}lon\\
Pernier 23} 
\email{alexandrodisla@hotmail.com}
\telephone{+50941483700}
\nofax{}
\lieu{Port-au-Prince}
\signature{}
%\signature{\begin{tabular}{@{}p{.5in}p{2in}@{}}
%		& \hrulefill \\
%		& \textbf{Alexandro Disla} \\
%		& Economiste-Planificateur au Minist\`{e}re de la Planification et de la Coop\'{e}ration Externe\\
%	\end{tabular}
%}

%\conc{Cover Letter}
 
\opening{Dear Sir or Madam,}

\begin{spacing}{1.5}

I am applying for the operations analyst position at the International Finance Corporation’s office in Haiti. I am an applied economist with several years of experience in economic analysis and database management. Most importantly, I have worked as modeling analyst at the Directorate of Economic and Social Planning of the Ministry of Planning and Extern Cooperation. 

I successfully completed my undergraduate studies at the School of Planning and Applied Economics (C.T.P.E.A). This rigorous training in applied economics gave me a sound knowledge of statistical methods, economic analysis and modeling. As analyst at the the Ministry of Planning and External Cooperation, I have developed  a critical thinking and an hands-on approach to understand and analyze key development in public policies and project management. Most importantly, I have periodically monitored the evolution of macroeconomic aggregates and I have participated in workshops on state budget together with the staff of the Ministry of Economy and Finance. Additionally, I was part of the team in charge of the Information and Development Planning Model which is a planing tool aiming to guide decision making and to improve governance in Haiti.

Given my experience in project management and my background in applied economics, I believe that I can bring valuable contribution to the C.L.A.H.T team. I am fluent in French and English and I have extensive experience of Microsoft Office, R, Python, JavaScript, MySQL and MongoDB.

I enjoy working in a dynamic and diverse work environment with colleagues from different nationalities and background. I take great pleasure in working on challenging projects as well as  participating in the decision-making process.

\end{spacing}

\closing{
    While requesting your attention to my application, please 
    accept, Madam, Sir, the expression of my respectful 
    consideration.}
\end{letter}
\end{document}
